%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry} % Document margins
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}}
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}

\name{Blaine C. Rieger} % Name
\address{76 Laurelhurst Drive} % Address L1
\address{Ladera Ranch, CA 92694} % Address L2
\address{949-636-9497 \\ blaine.rieger@gmail.com} % Phone and email

\begin{document}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}
									
	% LMU - Loyola Marymount University
	{\bf Loyola Marymount University, Los Angeles, California} \hfill {\bf August 2019 - Expected 2025}
	\\ {\em Master of Science, Electrical Engineering}
	\\ Graduate Thesis Title: "Modeling Driver Perception of Accelerator Pedal Input"
									
	% WPI - Worcester Polytechnic Institute  
	{\bf Worcester Polytechnic Institute, Worcester, Massachusetts} \hfill {\bf August 2012 - May 2016}  
	\\ {\em Bachelor of Science,  Electrical and Computer Engineering}
	\\ Undergraduate Major Qualification Project Title: "Smartphone-Based 12-Lead Electrocardiogram"
									
\end{rSection}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------
\begin{rSection}{Work Experience}

    % Novanta - Job History
    \begin{rSubsection}{Novanta, Irvine, California}{\bf November 2022 - August 2025}{Electrical Engineer}{}
        {\textbf{Novanta (Acquired Motion Solutions, January 2024)}} \hfill {\bf January 2024 - August 2025} \\
        {\textbf{Motion Solutions}} \hfill {\bf November 2022 - January 2024}
        \item Designed and integrated embedded control systems for precision electromechanical subsystems used in medical, life science, semiconductor, and defense applications.
        \item Developed multilayer PCB assemblies from schematic capture through fabrication and reflow; performed prototype troubleshooting, validation, and design revisions.
        \item Collaborated with electrical, mechanical, and automation teams to develop high-precision motion control systems and automated platforms.
        \item Performed motion stage tuning, accuracy verification, and repeatability testing using laser interferometry and precision metrology equipment.
        \item Supported production and assembly of in-house cable harnesses, ensuring build quality and inspection compliance in accordance with \textbf{IPC-A-610} and \textbf{IPC/WHMA-A-620} guidelines.
        \item Authored and maintained engineering documentation, including schematics, cable drawings, fixture layouts, and operational (O\&M) manuals to support traceability and quality control.
    \end{rSubsection}

    % Engineering Innovations - Job History
    \begin{rSubsection}{Engineering Innovations, Rancho Santa Margarita, California}{\bf September 2021 - November 2022}{Manufacturing Assistant}{}
        \item Operated and set up multi-axis vertical mills and lathes to manufacture precision components for government and commercial contracts, ensuring adherence to specifications.  
        \item Managed material inventory, optimizing stock levels to support uninterrupted production workflows.  
        \item Conducted thorough inspections of components, maintaining high quality and compliance with ISO standards, contractual, and regulatory requirements.  
    \end{rSubsection}

    % LMU - Job History
    \begin{rSubsection}{Loyola Marymount University, Los Angeles, California}{\bf May 2019 - December 2022}{Graduate Research Lab Assistant}{}
        \item Assisted in research at the Rehabilitation, Assistive Technology, and Human Control Theory (REACT) Lab, developing, fabricating, and testing electrical hardware and software for laboratory experiments.  
        \item Maintained simulators and test fixtures, ensuring reliable and accurate experimental setups.  
        \item Guided and supported undergraduate students in performing research studies, providing training on lab equipment, experimental procedures, and data collection.  
    \end{rSubsection}

	% Rye Electric Contract - Job History
    \begin{rSubsection}{Rye Electric, Rancho Santa Margarita, California}{\bf May 2020 - August 2021}{Engineering Consultant}{}
        \item Served as a technical advisor on prototype development of wearable devices undergoing the patent process.  
        \item Programmed and modeled components for early-stage prototypes, supporting design iteration and testing.  
        \item Led manufacturing and machining process development to enable scalable prototype production.  
    \end{rSubsection}

    % Rye Electric - Job History
    \begin{rSubsection}{Rye Electric, Rancho Santa Margarita, California}{\bf July 2016 - August 2018}{Project Engineer}{}
        \item Supported commercial electrical engineering projects in accordance with approved technical specifications and engineering drawings.  
        \item Provided on-site technical expertise, advising management on engineering decisions and resolving technical challenges.  
    \end{rSubsection}

	% Summer Internships
    \begin{rSubsection}{College Summer Internships}{}{Engineering Intern} {}
		\item {Rye Electric, Rancho Santa Margarita, California} \hfill{\bf June 2015 - August 2015}
		\item {Schneider Electric, Diamond Bar, California} \hfill{\bf June 2014 - August 2014}
		\item {Technologent, Irvine, California} \hfill{\bf June 2013 - August 2013}
		\item {Novak Electronics, Irvine, California} \hfill{\bf June 2012 - August 2012}        
	\end{rSubsection}

\end{rSection}

%\pagebreak

%----------------------------------------------------------------------------------------
%	Research Projects
%----------------------------------------------------------------------------------------
\begin{rSection}{Research Projects}

    \begin{rSubsection}{Tripoli Level 3 High Power Rocket}{\bf Present}{Personal Project - Level 3 Attempt Flight - Min. Total Impulse of 5,120.01 (N·s) - M Class Motor}{}
		\item  Develop bare-metal ARM based flight computer to log flight data and manage separation events during flight. Computer to be able to communicate tracking and telemetry via downlink to the base station. 
        \item Design and fabricate composite structural and aerodynamic components for the rocket. Simulate aerodynamic stability and performance with various payload and motor configurations.
	\end{rSubsection}
									
	\begin{rSubsection}{Modeling Driver Perception of Accelerator Pedal Input}{\bf Present}{Loyola Marymount Research Assistant / Master's Thesis}{}
		\item Design software and hardware to investigate the relationship between the perceived accelerator pedal application to the measured input
		\item Proposed solution will be a model from which a reference table can be readily derived 
	\end{rSubsection}
									
	\begin{rSubsection}{Smartphone-Based 12-Lead Electrocardiogram}{\bf December 2015}{Worcester Polytechnic Institute Major Qualifying Project}{}
		\item Designed ECG analog circuitry and PCB which was manufactured and populated with components 
		\item Interfaced analog PCB with embedded ARM processor to handle analog to digital conversion in addition to Bluetooth communication with smartphone
	\end{rSubsection}
									
	%\begin{rSubsection}{Aquaponic Greenhouse for an Urban Food Security Initiative}{\bf May 2015}{Worcester Polytechnic Institute Interactive Qualifying Project}{}
		%\item Built a functioning prototype growing system that would be used by a local community resource center
	%\end{rSubsection}
									
\end{rSection}

%\pagebreak

%----------------------------------------------------------------------------------------
%	publications
%----------------------------------------------------------------------------------------
\begin{rSection}{Publications}							
	\item Friedman, J., Murphy, S., and \bf Rieger, B.C. \normalfont ``Inexpensive, Portable, Smartphone-Based 12-Lead Electrocardiogram." \textit{Worcester Polytechnic University}, 2015.							
\end{rSection}

%----------------------------------------------------------------------------------------
%	certifications
%----------------------------------------------------------------------------------------
\begin{rSection}{Certifications}	
        \item \textbf{IPC-A-610 Acceptability of Electronic Assemblies \hfill{\bf 2025}}
        \item \textbf{IPCA-620 Requirements and Acceptance for Cable and Wire Harness Assemblies} \hfill{\bf 2025}
	\item \textbf{Tripoli Level 3 High-Power Rocketry} \hfill{\bf Expected Completion 2025}	
        \item \textbf{Tripoli Level 1 \& 2 High-Power Rocketry} \hfill{\bf 2015 - Recertify 2025}
\end{rSection}

%----------------------------------------------------------------------------------------
%	award scholarships 
%----------------------------------------------------------------------------------------
\begin{rSection}{Awards and Scholarships} \itemsep -2pt						
	\item \textbf{Shu Family Endowed Scholarship}, Academic Scholarship \hfill{\bf 2019 - 2020}
	\item \textbf{Edward J. and Mildred P. Sydor Scholarship}, Academic Scholarship \hfill{\bf 2013 - 2016}
	\item \textbf{Worcester Polytechnic Institute Scholarship}, Academic Scholarship \hfill{\bf 2012 - 2016}
	\item \textbf{Eagle Scout}, Boy Scouts of America \hfill{\bf 2011}							
\end{rSection}

%----------------------------------------------------------------------------------------
%	Skills
%----------------------------------------------------------------------------------------
\begin{rSection}{Skills} \itemsep -2pt						
	\item \textbf{Computer Software:} EDA (Kicad, Eagle), MATLAB, GNU Octave, IDE (Eclipse, STM32 Cube IDE), CAD (Solidworks, Fusion 360), Microsoft Office	
    \item \textbf{Programming Languages:} C, C++, Python, G-Code. Limited exposure to: (VHDL, Verilog, Assembly)
	\item \textbf{Communication Interfaces:} UART, I2C, I2S, SPI (SPI, QSPI), USB, CAN				
	\item \textbf{Lab Equipment:} Oscilloscope, Function Generator, Multimeter, Network Analyzer, Variable Power Supply, Soldering (Hand, Reflow)		
	\item \textbf{Fabrication:} PCB Assembly (Rigid / Flexible PCB , SMD / Through-Hole Components), Milling (Manual, CNC), Lathe (Manual, CNC), 3D Printing, Basic Welding (Arc, TIG, MIG), Various power and hand tools
\end{rSection}

\end{document}