%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry} % Document margins
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}}
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}

\name{Blaine C. Rieger}
\address{blaine.rieger@gmail.com $\cdot$ 949-636-9497} 
\address{Irvine, CA 92618} 
\address{U.S. Citizen $\cdot$ Eligible for Security Clearance}

\begin{document}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}
    
    % LMU - Loyola Marymount University
	{\bf Loyola Marymount University, Los Angeles, California} \hfill {\bf August 2019 - Expected 2025}
	\\ {\em Master of Science, Electrical Engineering}
	\\ Graduate Thesis Title: "Modeling Driver Perception of Accelerator Pedal Input"
    
    % WPI - Worcester Polytechnic Institute  
	{\bf Worcester Polytechnic Institute, Worcester, Massachusetts} \hfill {\bf August 2012 - May 2016}  
	\\ {\em Bachelor of Science,  Electrical and Computer Engineering}
	\\ Undergraduate Major Qualification Project Title: "Smartphone-Based 12-Lead Electrocardiogram"

\end{rSection}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------
\begin{rSection}{Work Experience}

    % Novanta - Job History
    \begin{rSubsection}{Novanta (Formerly Motion Solutions), Irvine, California}{November 2022 - August 2025}{Electrical Engineer}{}
        \item Designed and integrated embedded control systems for precision electromechanical subsystems in medical, life science, semiconductor, and defense applications.
        \item Developed and validated multi-layer PCBs; performed prototyping, troubleshooting, and design revisions.
        \item Collaborated with cross-functional teams on high-precision motion control systems and automated platforms.
        \item Tuned motion stages and verified accuracy/repeatability using laser interferometry and precision metrology.
        \item Supported cable harness assembly and inspection per IPC-A-610 and IPC/WHMA-A-620 standards.
        \item Authored and maintained schematics, cable drawings, fixture layouts, and operational manuals.
    \end{rSubsection}

    % Engineering Innovations - Job History
    \begin{rSubsection}{Engineering Innovations, Rancho Santa Margarita, California}{\bf September 2021 - November 2022}{Manufacturing Assistant}{}
        \item Operated and set up multi-axis vertical mills and lathes to manufacture precision components for government and commercial contracts, ensuring adherence to specifications.  
        \item Managed material inventory, optimizing stock levels to support uninterrupted production workflows.  
        \item Conducted thorough inspections of components, maintaining high quality and compliance with ISO standards, contractual, and regulatory requirements.  
    \end{rSubsection}

    % LMU - Job History
    \begin{rSubsection}{Loyola Marymount University, Los Angeles, California}{\bf May 2019 - December 2022}{Graduate Research Lab Assistant}{}
        \item Assisted in research at the Rehabilitation, Assistive Technology, and Human Control Theory (REACT) Lab, developing, fabricating, and testing electrical hardware and software for laboratory experiments.  
        \item Maintained simulators and test fixtures, ensuring reliable and accurate experimental setups.  
        \item Guided and supported undergraduate students in performing research studies, providing training on lab equipment, experimental procedures, and data collection.  
    \end{rSubsection}

	% Rye Electric Contract - Job History
    \begin{rSubsection}{Rye Electric, Rancho Santa Margarita, California}{\bf May 2020 - August 2021}{Engineering Consultant}{}
        \item Served as a technical advisor on prototype development of wearable devices undergoing the patent process.  
        \item Programmed and modeled components for early-stage prototypes, supporting design iteration and testing.  
        \item Led manufacturing and machining process development to enable scalable prototype production.  
    \end{rSubsection}

    % Rye Electric - Job History
    \begin{rSubsection}{Rye Electric, Rancho Santa Margarita, California}{\bf July 2016 - August 2018}{Project Engineer}{}
        \item Supported commercial electrical engineering projects in accordance with approved technical specifications and engineering drawings.  
        \item Provided on-site technical expertise, advising management on engineering decisions and resolving technical challenges.  
    \end{rSubsection}

    % Summer Internships
    %\begin{rSubsection}{College Summer Internships}{}{Engineering Intern} {}
        %\item {Rye Electric, Rancho Santa Margarita, California} \hfill{\bf June 2015 - August 2015}
        %\item {Schneider Electric, Diamond Bar, California} \hfill{\bf June 2014 - August 2014}
        %\item {Technologent, Irvine, California} \hfill{\bf June 2013 - August 2013}
        %\item {Novak Electronics, Irvine, California} \hfill{\bf June 2012 - August 2012}        
    %\end{rSubsection}

\end{rSection}

%----------------------------------------------------------------------------------------
%	Research Projects
%----------------------------------------------------------------------------------------
\begin{rSection}{Research Projects}

    % Level 3 Rocket - In Progress
    \begin{rSubsection}{Tripoli Level 3 High Power Rocket}{\bf Present}{Personal Project - Level 3 Attempt Flight - Min. Total Impulse of 5,120.01 (N·s) - M Class Motor}{}
        \item Developed an ARM-based embedded flight computer with battery management, deployment circuitry, avionics, and RF/GPS telemetry for real-time tracking.
        \item Designed and fabricated composite structural and aerodynamic components, simulating flight performance across motor and payload configurations to ensure stability and safety.
    \end{rSubsection}
    
    % LMU Research - HACTI Lab Thesis Project - In Progress
    \begin{rSubsection}{Modeling Driver Perception of Accelerator Pedal Input}{\bf Present}{Loyola Marymount Research Assistant / Master's Thesis}{}
        \item Designed and implemented hardware and software to investigate the relationship between drivers' perceived accelerator pedal input and the actual measured input.
        \item Developed a modeling framework capable of generating reference tables for practical application in vehicle control and driver behavior analysis.
    \end{rSubsection}
    
    % WPI MQP - 12 Lead EKG
    \begin{rSubsection}{Smartphone-Based 12-Lead Electrocardiogram}{\bf December 2015}{Worcester Polytechnic Institute Major Qualifying Project}{}
        \item Designed a multi-PCB ECG system with an analog front-end for signal acquisition, interfacing with an ARM microcontroller for analog-to-digital conversion and smartphone communication.
        \item Fabricated and assembled PCBs, including solder paste application, component placement, reflow, and rework, ensuring accurate ECG signal measurement and reliable system operation.
    \end{rSubsection}
    
    %\begin{rSubsection}{Aquaponic Greenhouse for an Urban Food Security Initiative}{\bf May 2015}{Worcester Polytechnic Institute Interactive Qualifying Project}{}
		%\item Built a functioning prototype growing system that would be used by a local community resource center
	%\end{rSubsection}
    
\end{rSection}

%----------------------------------------------------------------------------------------
%	publications
%----------------------------------------------------------------------------------------
\begin{rSection}{Publications}							
	\item Friedman, J., Murphy, S., and \bf Rieger, B.C. \normalfont ``Inexpensive, Portable, Smartphone-Based 12-Lead Electrocardiogram." \textit{Worcester Polytechnic University}, 2015.							
\end{rSection}

%----------------------------------------------------------------------------------------
%	certifications
%----------------------------------------------------------------------------------------
\begin{rSection}{Certifications}	
    \item \textbf{IPC-A-610 Acceptability of Electronic Assemblies \hfill{\bf 2025}}
    \item \textbf{IPC-A-620 Requirements and Acceptance for Cable and Wire Harness Assemblies} \hfill{\bf 2025}
	\item \textbf{Tripoli Level 3 High-Power Rocketry} \hfill{\bf Expected Completion 2026}	
    \item \textbf{Tripoli Level 1 \& 2 High-Power Rocketry} \hfill{\bf 2015 - Recertify 2025}
\end{rSection}

%----------------------------------------------------------------------------------------
%	award scholarships 
%----------------------------------------------------------------------------------------
\begin{rSection}{Awards and Scholarships} \itemsep -2pt						
	%\item \textbf{Shu Family Endowed Scholarship}, Academic Scholarship \hfill{\bf 2019 - 2020}
	%\item \textbf{Edward J. and Mildred P. Sydor Scholarship}, Academic Scholarship \hfill{\bf 2013 - 2016}
	%\item \textbf{Worcester Polytechnic Institute Scholarship}, Academic Scholarship \hfill{\bf 2012 - 2016}
	\item \textbf{Eagle Scout}, Boy Scouts of America \hfill{\bf 2011}							
\end{rSection}

%----------------------------------------------------------------------------------------
%	Skills
%----------------------------------------------------------------------------------------
\begin{rSection}{Skills} \itemsep -2pt
    \item \textbf{Embedded Systems:} STM32, AVR, and ARM Cortex-M microcontrollers; firmware development in C; SPI, I2C, CAN, UART, USB; board bring-up, debugging, and validation.
    \item \textbf{Hardware Design:} Analog/digital circuit design with op-amps, ADCs/DACs, sensors, and actuators; multi-layer PCB layout in KiCad, Eagle, Altium; Verilog and VHDL; fabrication, reflow and hand soldering, and prototype testing.
    \item \textbf{Testing \& Measurement:} Oscilloscopes, function generators, logic analyzers, VNAs; thermal and reliability testing; MATLAB and Python for data analysis.
    \item \textbf{Mechanical \& Prototyping:} 3D modeling in SOLIDWORKS/Fusion 360; rapid prototyping via 3D printing and machining; BOMs, assembly drawings, and documentation.
    \item \textbf{Standards \& Compliance:} IPC/WHMA, ISO, and MIL-STD practices.
\end{rSection}

\end{document}